### 2018-04-18 reports/thesis/chapters/5_inference.tex
Adjusted harshness in NoDefect_Sinusoid, proof read inference chapter.

The aim of this project is to obtain an x-ray image of a 3D printed sample and compare it with a simulation of that scan using software called \texttt{aRTist}. \texttt{aRTist} can simulate x-ray scans of the 3D printed sample given the specifications of the scan, such as the x-ray source, the x-ray detector and the blueprint of the 3D printed sample. Users of \texttt{aRTist} can align the simulated x-ray image to the real x-ray image using numerical methods, however this is outside the scope of this thesis.

Disagreement between the scan and \texttt{aRTist} can be found by simply subtracting one image from the other, any values too big in magnitude can be considered as a defect. However in the previous chapters, it was found that x-ray photons behave randomly and large differences in the comparison can be due to chance. Thus the comparisons should be done under the face of uncertainty.

A pixel by pixel inference was proposed to do defect detection. A statistic $z_{i,j}$ for the $(i,j)$ positioned pixel can be calculated for all pixels. This statistic is
\begin{equation}
    z_{i,j} = 
    \dfrac{
        \text{scan}_{i,j} - \text{aRTist}_{i,j}
    }
    {
        \sqrt{\widehat{\variance}\left[\text{scan}_{i,j}\right]}
    }
\end{equation}
where $\widehat{\variance}\left[\text{scan}_{i,j}\right]$ is the estimated grey value variance of pixel $(i,j)$ in the scan. Under mild assumptions, it was shown in the previous chapters that the grey values in the scan are Normal. Thus by treating the simulated image from \texttt{aRTist} as known, then
\begin{equation}
z_{i,j}\sim \normal(0,1) \ .
\end{equation}
This means the randomness of the $z_{i,j}$ statistics can be quantified.

The estimation of the grey value variance, that is $\widehat{\variance}\left[\text{scan}_{i,j}\right]$ will be explained here. The variance model can be calibrated, or trained, by holding out a number replicated x-ray scans of a 3D printed sample. These replicated x-ray scans provide variance-mean data which then can be used to train the variance model, such as a Gamma distributed GLM. The method on doing so was described in the previous chapter and it was found a linear relationship between the variance and the mean was a good model. The variance was then predicted using the grey value in the \texttt{aRTist} simulation.

This method for inference can be applied to the dataset \texttt{Sep16 120deg}. The 20 x-ray images were spilt into 2. 19 images were used to train the variance-mean model. One image, called the test image, was used to compare with \texttt{aRTist}, as shown in Figure \ref{fig:inference_initial_artist_scan_aRTist}.

@@

For each pixel, a $z_{i,j}$ statistic was calculated. A $z_{i,j}$ statistic too large in magnitude can be considered to be evidence of a positive result. Another way to represent the $z_{i,j}$ statistic is the $p$-value which is given as
\begin{equation}
    p_{i,j} = 2(1-\Phi(\|z_{i,j}\|))
\end{equation}
which can takes values $0\leqslant p_{i,j} \leqslant 1$. A $p$-value too small is considered to be evidence of a positive result. The result $z$ statistics and $p$-values are shown in Figure \ref{fig:inference_initial_artist_logp_z}.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/initial_artist_logp.eps}
        \caption{$-\log p\text{-values}$}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/initial_artist_z_image.eps}
        \caption{$z$ statistics}
    \end{subfigure}
    }
    \caption{The resulting z statistics and $p$ values comparing an x-ray scan with the \texttt{aRTist} simulation.}
    \label{fig:inference_initial_artist_logp_z}
\end{figure}

The resulting $z$ statistics and $p$-values are concerning. This is because the $p$-values are not very smooth on the surfaces of the sample. It should be expected that small $p$-values are in areas of the defects. Significant pixels were chosen for $\|z\|>\input{../tables/initial_artist_z_critical.txt}$, this value was chosen by using the \cite{benjamini1995controlling} (BH) procedure at the $z_\alpha = 2$ significance level. The significant pixels are shown in Figure \ref{fig:inference_initial_artist_sig_pixels}.

@@

Model misspecification appears to be the main source of error. The $z$ statistics can be inspected using a histogram or a QQ plot, as shown in Figure \ref{fig:inference_initial_artist_z_histo}. It can be seen that the $z$ statistics do not look Normal which seems to suggest that the assumption of $z_{i,j}\sim \normal(0,1)$ is incorrect. However this assumption can relaxed and can be done using the empirical null \citep{efron2004large}.

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{../figures/inference/initial_artist_sig_pixels.eps}
    \caption{Significant pixels highlighted at the $z_\alpha = 2$ significance level.}
    \label{fig:inference_initial_artist_sig_pixels}
\end{figure}

\begin{figure}
    \centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
    	\includegraphics[width=\textwidth]{../figures/inference/initial_artist_z_histo.eps}
    	\caption{Histogram}
    \end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
    	\includegraphics[width=\textwidth]{../figures/inference/initial_artist_z_qq.eps}
    	\caption{QQ plot}
    \end{subfigure}
	}
    \caption{Distribution of the  $z$ statistics with the BH procedure critical region}
    \label{fig:inference_initial_artist_z_histo}
\end{figure}

This chapter will cover hypothesis testing, for a single test and then for multiple tests. The empirical null will then be reviewed which then can be extended to an image filter, called the empirical null filter. This filter will adjust each $z$ statistic according to its neighbours, ironing out false positive results. Simulations and actual results will be shown at the end of the chapter.

@@

Hypothesis testing dates back to \cite{pearson1900on}, \cite{neyman1933on} and \cite{fisher1970statistical}. It is so fundamental in science that it is now taught in schools.

The focus on this section is on the single hypothesis test. Here the random variable $Z\sim\normal(\mu,1)$ will be studied here as this is of interest in this project. It also appears in other tests such as the difference in sample means.

In the context of this project, an example of hypothesis testing will be given here. Here, it was assumed that $Z\sim\normal(0,1)$. A null hypothesis can be written down to describe this
\begin{equation}
    H_0:\mu=0 \ .
\end{equation}
It specifies the assumptions made on the random variable $Z$. Any data behaving as assumed is treated as a negative result.

A positive result is obtained when unlikely data is obtained and this happens if $Z$ deviates too much from 0. This can be described as testing $H_0$ against an alternative hypothesis $H_1$ where
\begin{equation}
    H_1:\mu\neq0 \ .
\end{equation}
How much $Z$ deviates from 0 to be considered a positive is up to the user but typically $\|Z\|>z_\alpha$ where $z_\alpha =2$ is considered significant.

A way to quantify the threshold for a positive result is to use something called the size of the test, otherwise known as the significance level, denoted as $\alpha$. This is the probability of a false positive result, which can be denoted as
\begin{equation}
    \prob(\|Z\|>z_\alpha|H_0) = \alpha \ .
\end{equation}
Using the fact the Normal distribution is symmetric then
\begin{equation}
    2(1 - \Phi(z_\alpha)) = \alpha \ .
    \label{eq:inference_single_alpha}
\end{equation}
The choice of $z_\alpha=2$ will set the size of the test to be $\alpha\approx 4.55\%$. This sort of choice of threshold and size is sensible.

@@

In this section, the single hypothesis test will be extended and the multiple hypothesis testing \citep{shaffer1995multiple, dudoit2003multiple} shall be reviewed.

Suppose $n$ test statistics were obtained $Z_1,Z_2,\dotdotdot,Z_n$ where $Z_i\sim\normal(\mu,1)$ for $i=1,2,\dotdotdot,n$ and i.i.d. One can test each of these statistics for the following hypotheses $H_0:\mu=0$ and $H_1:\mu\neq 0$. Using the method from the single hypothesis test at the $z_\alpha=2$ level, any statistic where $\|Z_i\|>2$ for $i=1,2,\dotdotdot,n$ would be considered a positive result.

@@

While the uncorrected method for multiple hypothesis testing has it flaws, it does control the per comparison error rate (PCER) \citep{benjamini1995controlling}. PCER is the proportion of false positives out of all tests. There are corrections for multiple hypothesis testing which controls different things. Conventionally they are expressed in terms of the number of errors made in testing, these are defined in Table \ref{table:inference_randomvariables}. Using the notation, formally PCER is defined as
\begin{equation}
    \text{PCER}=
    \dfrac{
        1
    }
    {
        n
    }
    \expectation[V]
    \ .
\end{equation}
It can be seen that if the uncorrected test controls the false positive rate such that $\expectation[V]/n_0 = \alpha$, then it controls the PCER such that
\begin{equation}
    \text{PCER}\leqslant\alpha \ .
\end{equation}

\begin{table}
    \centering
    \begin{tabular}{c|c|c|c}
        &Negative&Positive&Total\\\hline
        True null & $U$ & $V$ & $n_0$\\
        Non-true null & $T$ & $S$ & $n-n_0$\\\hline
        &$n-R$&$R$&$n$
    \end{tabular}
    \caption{Random variable definitions for the different types of error made in multiple hypothesis testing}
    \label{table:inference_randomvariables}
\end{table}

The Bonferroni correction \citep{shaffer1995multiple, bland1995multiple, perneger1998what} controls the FWER. This is done by adjusting the size of the test to be $\alpha/n$. By using the adjusted size, Equation \eqref{eq:inference_fwer} becomes
\begin{equation}
    \text{FWER}=1-\left[(1-\alpha/n)^n\right]\ .
\end{equation}
Using the approximation $(1-\alpha/n)^n\approx = 1-\alpha$ then
\begin{equation}
    \text{FWER}\approx \alpha \ .
\end{equation}
This shows that the Bonferroni correction controls the family-wise error rate such that
\begin{equation}
    \text{FWER} \leqslant \alpha \ .
\end{equation}
However in practice the Bonferroni correction is not very powerful \citep{perneger1998what}, meaning it does give too many false negative results. This is because the correction traded too many false positives for false negatives.

The \cite{benjamini1995controlling} (BH) procedure controls the false discovery rate (FDR) \citep{benjamini2010discovering} rather than the false positive or family-wise rate. The FDR is the proportion of false positives out of all positive results, that is
\begin{equation}
    \text{FDR} = \expectation\left[
        \dfrac{V}{R}
    \right]
    \ .
\end{equation}
It is defined that $V/R=0$ when $R=0$.

@@

The procedure is as follows. Suppose $n$ test statistics were obtained $Z_1,Z_2,\dotdotdot,Z_n$. They will need to be converted to $p$-values and ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \dotdotdot \leqslant p_{(n)}$. The adjusted size $\alpha_{\text{BH}}$ is
\begin{equation}
    \alpha_{\text{BH}} = \frac{\alpha k}{n}
\end{equation}
where
\begin{equation}
    k\text{ is the largest }i\text{ for which }p_{(i)}\leqslant\frac{i}{n}\alpha
    \ .
\end{equation}
This essentially declare $p_{(1)},p_{(2)},\dotdotdot,p_{(k)}$ as positive results. For the case where $p_{(1)}>\alpha/n$, then $k=1$ shall be chosen so that the Bonferroni correction is used instead. The BH procedure comes from the fact that assuming the null hypothesis is true for all $Z_i$ and all tests are independent, then the $p$-values are uniformly distributed \citep{simes1986improved}. However it can be shown that the BH procedure works for many scenarios of dependencies \citep{benjamini2001control}.

@@

A few numerical examples will be shown here to explore the properties of the 3 different types of methods to do multiple hypothesis testing. Two scenarios will be shown here. In the first case, 1\,000 $\normal(0,1)$ independent test statistics were simulated, all test statistics are all null. In the second case, 800 null $\normal(0,1)$ and 200 alternative $\normal(2,1)$ independent test statistics were simulated.

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{../figures/inference/multi_test_nullhisto.eps}
	\caption{A histogram of simulated of 1\,000 null test statistics. Also provided are the critical boundaries at the $z_\alpha=2$ level, one uncorrected for multiple testing, another corrected using the Bonferroni correction.}
	\label{fig:inference_multi_test_nullhisto}
\end{figure}

A histogram of the test statistics in the all null case is shown in Figure \ref{fig:inference_multi_test_nullhisto}. The critical boundaries are also shown. In the uncorrected case, the critical region is $\|Z\|>2$. Using the Bonferroni correction, the critical region becomes $\|Z\|>4.08...$. By inspection of the histogram, the uncorrected method tested a number of test statistics to be positive and falsely so. The Bonferroni correction performs well because it tested all the test statistics as negative correctly.

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{../figures/inference/multi_test_nullpvalues.eps}
	\caption{Ordered $p$-values of simulated 1\,000 null test statistics. Any values below the critical line are declared positive using the BH procedure.}
	\label{fig:inference_multi_test_nullpvalues}
\end{figure}

The ordered $p$-values are shown in Figure \ref{fig:inference_multi_test_nullpvalues}. The $p$-values form a straight line as a result of being uniformly distributed. The critical line is $0.0455...\times\text{order}/1\,000$. This corresponds to the BH procedure and $p$-values below where the 2 curves intersect are considered positive results. In the all null case, the $p$-values are all larger than the critical line, thus no test statistic were tested positive using the BH procedure. As a result, the Bonferroni and BH procedure tested all test statistics to be negative correctly.

\begin{figure}
	\centering
	\includegraphics[width = 0.8\textwidth]{../figures/inference/multi_test_althisto.eps}
	\caption{A histogram of simulated of 800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ test statistics. Also provided are the critical boundaries at the $z_\alpha=2$ level using no correction, Bonferroni correction and the BH procedure.}
	\label{fig:inference_multi_test_althisto}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{../figures/inference/multi_test_altpvalues.eps}
    \caption{Ordered $p$-values of simulated 800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ test statistics. Any values below the critical line are declared positive using the BH procedure.}
	\label{fig:inference_multi_test_altpvalues}
\end{figure}

In the second scenario, 800 $\normal(0,1)$ and 200 $\normal(2,1)$ test statistics were simulated. The histogram of the simulated test statistics, along with the critical regions, is shown in Figure \ref{fig:inference_multi_test_althisto}. The uncorrected and Bonferroni corrected critical regions are still the same as the first scenario. However this time the critical region using the BH procedure is different, it is $\|Z\|\geqslant\input{../tables/multi_test_alt_z_critical.txt}$.

The ordered $p$-values are shown in Figure \ref{fig:inference_multi_test_altpvalues}. There are $p$-values below the critical line according to the BH procedure, testing $\input{../tables/multi_test_alt_n_positive_bh.txt}$ test statistics as positive. The uncorrected test tested $\input{../tables/multi_test_alt_n_positive_uncorrected.txt}$ test statistics as positive.

@@

Unfortunately not all 200 non-null test statistics were tested as positive, statisticians would describe it as not powerful. This is however unavoidable as a number of null and non-null test statistics will be similar in value. The aim of hypothesis testing is not to classify positive and negative results correctly, but rather highlight a number of test statistics which are worth investigating.

The error rates can be estimated as a result of knowing whenever each test statistic is truly null or non-null. Suppose the simulation was repeated $N$ times and $r_1,r_2,\dotdotdot,r_N$ number of test statistics were observed to be tested positive. From these positive results, suppose in addition that $v_1,v_2,\dotdotdot,v_N$ false positives were observed. In other words, they are realisations of the random variables defined in Table \ref{table:inference_randomvariables}. The error rates can be estimated
\begin{equation}
	\widehat{\text{PCER}} = \frac{1}{Nn}\sum_{i=1}^N v_i
\end{equation}
\begin{equation}
	\widehat{\text{FWER}} = \frac{1}{N} \sum_{i=1}^N \mathbb{I}(v_i\neq 0)
\end{equation}
\begin{equation}
	\widehat{\text{FDR}} = \frac{1}{N}\sum_{i=1}^N\dfrac{v_i}{r_i}\times\mathbb{I}(r_i\neq0)
	\ .
\end{equation}
The estimates of PCER and FDR is esentially the sample mean, so the standard error can be used to quantify the error. For the FWER, the variance of the Beta distribution is used to quantify the error
\begin{equation}
	\text{standard error of }\widehat{\text{FWER}} = 
	\sqrt{\dfrac{ab}{(a+b)^2(a+b+1)}}
\end{equation}
where $a = \sum_{i=1}^N \mathbb{I}(v_i\neq 0)$ and $b = N - a$.

\begin{table}
    \centering
    \input{../tables/inference_error_rate1.txt}
    \caption{Various error rates when using different types of corrections for multiple hypothesis testing at the $z_\alpha=2$ level. 1\,000 test statistics were simulated, all standard Normal. Error bars represent the standard errors after 1\,000 repeats of the experiment.}
    \label{table:inference_error_rate1}
\end{table}

\begin{table}
    \centering
    \input{../tables/inference_error_rate2.txt}
    \caption{Various error rates when using different types of corrections for multiple hypothesis testing at the $z_\alpha=2$ level. 1\,000 test statistics were simulated, 800 from the standard Normal, 200 from $\normal(2,1)$. Error bars represent the standard errors after 1\,000 repeats of the experiment.}
     \label{table:inference_error_rate1}
\end{table}

>>>>

The aim of this project was to obtain an x-ray image of a 3D printed sample and compare it with a simulation of that scan using software called \texttt{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. \texttt{aRTist} can simulate x-ray scans of the 3D printed sample given the specifications of the scan, such as the x-ray source, the x-ray detector and the blueprint of the 3D printed sample \citep{bellon2011simulation, deresch2012simulating}. Users of \texttt{aRTist} can align the simulated x-ray image to the real x-ray image using numerical methods, however this is outside the scope of this thesis.

Disagreement between the scan and \texttt{aRTist} can be found by simply subtracting one image from the other, any values too big in magnitude can be considered as a defect. However in the previous chapters, it was found that x-ray photons behave randomly and differences in the comparison can be due to chance. Thus the comparisons should be done under the face of uncertainty.

A pixel by pixel inference was proposed to do defect detection. A statistic $z_{x,y}$ for the $(x,y)$ positioned pixel was calculated for all pixels. This statistic is
\begin{equation}
    Z_{x,y} = 
    \dfrac{
        \text{scan}_{x,y} - \text{aRTist}_{x,y}
    }
    {
        \sqrt{\widehat{\variance}\left[\text{scan}_{x,y}\right]}
    }
\end{equation}
where $\widehat{\variance}\left[\text{scan}_{x,y}\right]$ is the estimated grey value variance of pixel $(x,y)$ in the scan. Under mild assumptions, it was shown in the previous chapters that the grey values in the scan were Normal. Thus by treating the simulated image from \texttt{aRTist} as known and the ground truth, then the randomness of the $z_{i,j}$ statistics can be quantified
\begin{equation}
Z_{i,j}\sim \normal(0,1) \ .
\end{equation}
As with usual statistical convention, upper case $Z$ denote a random variable. Whereas lower case $z$ denote a realisation or an observation of that random variable.

The estimation of the grey value variance, that is $\widehat{\variance}\left[\text{scan}_{i,j}\right]$ is be explained here. The variance model can be calibrated, or trained, by holding out a number replicated x-ray scans of a 3D printed sample. These replicated x-ray scans provide variance-mean data which was used to train the variance model, such as a Gamma distributed GLM. The method on doing so was described in the previous chapter and it was found a linear relationship between the variance and the mean was a good model. The variance was then predicted using the grey value in the \texttt{aRTist} simulation.

This method for inference was applied to the dataset \texttt{Sep16 120deg}. Here a cuboid with voids were purposefully manufactured to see if they can be detected. The 20 x-ray images were spilt into 2. 19 images were used to train the variance-mean model. One image, called the test image, was used to compare with \texttt{aRTist}, as shown in Figure \ref{fig:inference_initial_artist_scan_aRTist}. In the \texttt{aRTist} simulation, the software did a simulation as if the voids were not there.

@@

For each pixel, a $z$ statistic was calculated. A $z$ statistic too large in magnitude can be considered to be evidence of a positive result. Another way to represent the $z$ statistic is the $p$-value which is given as
\begin{equation}
    p_{x,y} = 2(1-\Phi(\|z_{x,y}\|))
\end{equation}
which can takes values $0\leqslant p_{i,j} \leqslant 1$. A $p$-value too small is considered to be evidence of a defect. The resulting $z$ statistics and $p$-values are shown in Figure \ref{fig:inference_initial_artist_logp_z}.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/initial_artist_logp.eps}
        \caption{$-\log p\text{-values}$}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/initial_artist_z_image.eps}
        \caption{$z$ statistics}
    \end{subfigure}
    }
    \caption{The resulting $z$ statistics and $p$ values comparing an x-ray scan with the \texttt{aRTist} simulation.}
    \label{fig:inference_initial_artist_logp_z}
\end{figure}

The resulting $z$ statistics and $p$-values are concerning. This is because the $p$-values are not very smooth on the surfaces of the sample. It should be expected that small $p$-values are in areas of the defects. Pixels are significant, or considered to be evidence of a defect, when for $\|z_{x,y}\|>\input{../tables/initial_artist_z_critical.txt}$, this value was chosen by using the \cite{benjamini1995controlling} (BH) procedure at the $z_\alpha = 2$ significance level. The significant pixels are shown in Figure \ref{fig:inference_initial_artist_sig_pixels}.

@@

Model misspecification appeared to be the main source of error. The $z$ statistics was inspected using a histogram and a QQ plot, as shown in Figure \ref{fig:inference_initial_artist_z_histo}. It can be seen that the $z$ statistics does not look Normal which seems to suggest that the assumption of $z_{i,j}\sim \normal(0,1)$ is incorrect. However this assumption can relaxed and can be done using the empirical null \citep{efron2004large}.

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{../figures/inference/initial_artist_sig_pixels.eps}
    \caption{Significant pixels highlighted using the BH procedure at the $z_\alpha = 2$ significance level.}
    \label{fig:inference_initial_artist_sig_pixels}
\end{figure}

\begin{figure}
    \centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
    	\includegraphics[width=\textwidth]{../figures/inference/initial_artist_z_histo.eps}
    	\caption{Histogram}
    \end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
    	\includegraphics[width=\textwidth]{../figures/inference/initial_artist_z_qq.eps}
    	\caption{QQ plot}
    \end{subfigure}
	}
    \caption{Distribution of the  $z$ statistics with the BH procedure critical region at the $z_\alpha=2$ level.}
    \label{fig:inference_initial_artist_z_histo}
\end{figure}

This chapter covers hypothesis testing, for a single test and then for multiple tests, treating each pixel as a test. The empirical null is reviewed and then extended to an image filter, called the empirical null filter. This filter adjust each $z$ statistic according to its neighbours, ironing out false positive results. Simulations and actual results was shown at the end of the chapter.

@@

Hypothesis testing dates back to \cite{pearson1900on}, \cite{neyman1933on} and \cite{fisher1970statistical}. It is one of the most fundamental methods in science.

The focus on this section is on the single hypothesis test. A Normal random variable is studied as this is of interest in this project. It also appears in other tests such as the difference in sample means.

In the context of this project, an example of hypothesis testing is given here. Here, it was assumed that the test statistic $Z\sim\normal(0,1)$. A null hypothesis is written down to describe this. This is done by specifying the random variable as $Z\sim\normal(\mu,1)$ and the null hypothesis
\begin{equation}
    H_0:\mu=0 \ .
\end{equation}
This specifies the assumptions made on the random variable $Z$, here the mean is zero. Any data behaving as assumed is treated as a negative result or not significant.

A positive, or significant, result is obtained when unlikely data is obtained and this happens if $Z$ deviates too much from 0. This can be described as testing $H_0$ against an alternative hypothesis $H_1$ where
\begin{equation}
    H_1:\mu\neq0 \ .
\end{equation}
How much $Z$ deviates from 0 to be considered a positive is up to the user but typically $\|Z\|>z_\alpha$ where $z_\alpha =2$ is a typical choice for the threshold.

A way to quantify the threshold for a positive result is to use something called the size of the test, otherwise known as the significance level, denoted as $\alpha$. This is the probability of a false positive result, which can be denoted as
\begin{equation}
    \prob(\|Z\|>z_\alpha|H_0) = \alpha \ .
\end{equation}
Using the fact the Normal distribution is symmetric then
\begin{equation}
    2(1 - \Phi(z_\alpha)) = \alpha \ .
    \label{eq:inference_single_alpha}
\end{equation}
The choice of $z_\alpha=2$ set the size of the test to be $\alpha\approx 4.55\%$. The $z_\alpha=2$ level is used throughout this project.

@@

In this section, the single hypothesis test is extended and the multiple hypothesis testing \citep{shaffer1995multiple, dudoit2003multiple} is reviewed.

Suppose $n$ test statistics were obtained $Z_1,Z_2,\dotdotdot,Z_n$ where $Z_i\sim\normal(\mu,1)$ for $i=1,2,\dotdotdot,n$ and i.i.d. Suppose each individual statistic were used to test the following hypotheses $H_0:\mu=0$ and $H_1:\mu\neq 0$. Using the method from the single hypothesis test at the $z_\alpha=2$ level, any statistic where $\|Z_i\|>2$ for $i=1,2,\dotdotdot,n$ would be considered significant.

@@

While the uncorrected method for multiple hypothesis testing has it flaws, it does control the per comparison error rate (PCER) \citep{benjamini1995controlling}. PCER is the proportion of false positives out of all tests. There are corrections for multiple hypothesis testing which controls different things. Conventionally they are expressed in terms of the number true/false positives/negatives, these are defined in Table \ref{table:inference_randomvariables}. Using the notation, formally PCER is defined as
\begin{equation}
    \text{PCER}=
    \dfrac{
        1
    }
    {
        n
    }
    \expectation[V]
    \ .
\end{equation}
It can be seen that if the uncorrected test controls the false positive rate such that $\expectation[V]/n_0 = \alpha$, then it controls the PCER such that
\begin{equation}
    \text{PCER}\leqslant\alpha \ .
\end{equation}

\begin{table}
    \centering
    \begin{tabular}{c|c|c|c}
        &Negative&Positive&Total\\\hline
        True null & $U$ & $V$ & $n_0$\\
        Non-true null & $T$ & $S$ & $n-n_0$\\\hline
        &$n-R$&$R$&$n$
    \end{tabular}
    \caption{Random variable definitions for true/false positives/negatives made in multiple hypothesis testing}
    \label{table:inference_randomvariables}
\end{table}

The Bonferroni correction \citep{shaffer1995multiple, bland1995multiple, perneger1998what} controls the FWER. This is done by adjusting the size of the test to be $\alpha/n$. By using the adjusted size, Equation \eqref{eq:inference_fwer} becomes
\begin{equation}
    \text{FWER}=1-\left[(1-\alpha/n)^n\right]\ .
\end{equation}
Using the approximation $(1-\alpha/n)^n\approx = 1-\alpha$ then
\begin{equation}
    \text{FWER}\approx \alpha \ .
\end{equation}
This shows that the Bonferroni correction controls the family-wise error rate such that
\begin{equation}
    \text{FWER} \leqslant \alpha \ .
\end{equation}
However in practice the Bonferroni correction is not very powerful \citep{perneger1998what}, meaning it does give too many false negatives. This is because the correction traded too many false positives for false negatives.

The \cite{benjamini1995controlling} (BH) procedure controls the false discovery rate (FDR) \citep{benjamini2010discovering} rather than the PCER or FWER. The FDR is the proportion of false positives out of all positive results, that is
\begin{equation}
    \text{FDR} = \expectation\left[
        \dfrac{V}{R}
    \right]
    \ .
\end{equation}
It is defined that $V/R=0$ when $R=0$.

@@

The procedure is as follows. Suppose $n$ test statistics were obtained $Z_1,Z_2,\dotdotdot,Z_n$. They are converted to $p$-values and ordered such that $p_{(1)}\leqslant p_{(2)}\leqslant \dotdotdot \leqslant p_{(n)}$. Suppose a size $\alpha$ is provided beforehand. The size is then adjusted to
\begin{equation}
    \alpha_{\text{BH}} = \frac{\alpha k}{n}
\end{equation}
where
\begin{equation}
    k\text{ is the largest }i\text{ for which }p_{(i)}\leqslant\frac{i}{n}\alpha
    \ .
\end{equation}
This essentially declare $p_{(1)},p_{(2)},\dotdotdot,p_{(k)}$ as significant. For the case where $p_{(1)}>\alpha/n$, then $k=1$ was chosen so that the Bonferroni correction is used instead. The BH procedure comes from the fact that assuming the null hypothesis is true for all $Z_i$ and all tests are independent, then the $p$-values are uniformly distributed \citep{simes1986improved}. However it can be shown that the BH procedure works for many scenarios of dependencies \citep{benjamini2001control}.

@@

A few numerical examples is shown here to explore the properties of the 3 different types of methods to do multiple hypothesis testing. Two scenarios is shown here. In the first case, 1\,000 $\normal(0,1)$ independent test statistics were simulated, all test statistics were null. In the second case, 800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ independent test statistics were simulated.

A histogram of the test statistics in the all null case is shown in Figure \ref{fig:inference_multi_test_nullhisto_pvalues}. The critical boundaries are also shown. In the uncorrected case, the critical region is $\|Z\|>2$. Using the Bonferroni correction, the critical region becomes $\|Z\|>4.08...$. By inspection of the histogram, the uncorrected method tested a number of test statistics to be positive and falsely so. The Bonferroni correction performs well because it tested all the test statistics as negative correctly.

The ordered $p$-values are shown in Figure \ref{fig:inference_multi_test_nullhisto_pvalues}. The $p$-values form a straight line as a result of being uniformly distributed. The critical line is $0.0455...\times\text{order}/1\,000$ using the BH procedure. In the all null case, the $p$-values are all larger than the critical line, thus no test statistic were tested positive using the BH procedure. As a result, the Bonferroni and BH procedure tested all test statistics to be negative correctly.

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.8\textwidth}
    	\includegraphics[width=\textwidth]{../figures/inference/multi_test_nullhisto.eps}
    	\caption{Histogram}
    \end{subfigure}
	\begin{subfigure}[b]{0.8\textwidth}
    	\includegraphics[width=\textwidth]{../figures/inference/multi_test_nullpvalues.eps}
    	\caption{Ordered $p$-values}
    \end{subfigure}
    \caption{1\,000 null test statistics were simulated. a) Critical boundaries are shown at the $z_\alpha=2$ level, one uncorrected for multiple testing, another corrected using the Bonferroni correction. b) Any values below the critical line are declared significant using the BH procedure.}
    \label{fig:inference_multi_test_nullhisto_pvalues}
\end{figure}

In the second scenario, 800 $\normal(0,1)$ and 200 $\normal(2,1)$ test statistics were simulated. The histogram of the simulated test statistics, along with the critical regions, is shown in Figure \ref{fig:inference_multi_test_althisto_pvalues}. The uncorrected and Bonferroni corrected critical regions are still the same as the first scenario. However this time the critical region using the BH procedure is different, it is $\|Z\|\geqslant\input{../tables/multi_test_alt_z_critical.txt}...$.

The ordered $p$-values are shown in Figure \ref{fig:inference_multi_test_althisto_pvalues}. There are $p$-values below the critical line according to the BH procedure. $p$-values below where the curves intersect are considered significant, testing $\input{../tables/multi_test_alt_n_positive_bh.txt}$ test statistics as positive. The uncorrected test tested $\input{../tables/multi_test_alt_n_positive_uncorrected.txt}$ test statistics as positive.

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.8\textwidth}
    	\includegraphics[width=\textwidth]{../figures/inference/multi_test_althisto.eps}
    	\caption{Histogram}
    \end{subfigure}
	\begin{subfigure}[b]{0.8\textwidth}
    	\includegraphics[width=\textwidth]{../figures/inference/multi_test_altpvalues.eps}
    	\caption{Ordered $p$-values}
    \end{subfigure}
    \caption{800 null $\normal(0,1)$ and 200 non-null $\normal(2,1)$ test statistics were simulated. a) Critical boundaries are shown at the $z_\alpha=2$ level, one uncorrected for multiple testing, another corrected using the Bonferroni correction. b) Any values below the critical line are declared significant using the BH procedure.}
    \label{fig:inference_multi_test_althisto_pvalues}
\end{figure}

@@

Unfortunately not all 200 non-null test statistics were tested as positive, statisticians would describe it as not powerful. This is however unavoidable as a number of null and non-null test statistics will be similar in value. The aim of hypothesis testing is not to classify positive and negative results correctly, but rather highlight a number of test statistics which are worth investigation.

The error rates can be estimated as a result of knowing whenever each test statistic is truly null or non-null. Suppose the simulation was repeated $N$ times and $r_1,r_2,\dotdotdot,r_N$ number of test statistics were observed to be tested positive. From these positive results, suppose in addition that $v_1,v_2,\dotdotdot,v_N$ false positives were observed. In other words, they are realisations of the random variables defined in Table \ref{table:inference_randomvariables}. The error rates can be estimated
\begin{equation}
	\widehat{\text{PCER}} = \frac{1}{Nn}\sum_{i=1}^N v_i
\end{equation}
\begin{equation}
	\widehat{\text{FWER}} = \frac{1}{N} \sum_{i=1}^N \mathbb{I}(v_i\neq 0)
\end{equation}
\begin{equation}
	\widehat{\text{FDR}} = \frac{1}{N}\sum_{i=1}^N\dfrac{v_i}{r_i}\times\mathbb{I}(r_i\neq0)
	\ .
\end{equation}
The estimates of PCER and FDR is essentially the sample mean, so the standard error can be used to quantify the error. For the FWER, the standard error was chosen to be
\begin{equation}
	\text{standard error of }\widehat{\text{FWER}} = 
	\sqrt{\dfrac{ab}{(a+b)^2(a+b+1)}}
\end{equation}
where $a = \sum_{i=1}^N \mathbb{I}(v_i\neq 0)$ and $b = N - a$. Without going into too much detail, this comes from setting a prior $\text{FWER}\sim\betaDist(0,0)$ and assuming that $\mathbb{I}(V\neq0)\sim\bernoulli(\text{FWER})$. The posterior distribution is $\text{FWER}|V_1,V_2,\dotdotdot V_N\sim\betaDist(a,b)$ and the variance was used for the standard error.

\begin{table}
    \centering
    \begin{subtable}{\textwidth}
    	\centering
    	\input{../tables/inference_error_rate1.txt}
    	\caption{1\,000 $\normal(0,1)$}
    \end{subtable}
    \begin{subtable}{\textwidth}
    	\centering
    	\input{../tables/inference_error_rate2.txt}
    	\caption{800 $\normal(0,1)$ and 200 $\normal(2,1)$}
    \end{subtable}
    \caption{Various error rates when using different types of corrections for multiple hypothesis testing at the $z_\alpha=2$ level. 1\,000 test statistics were simulated, in a) all test statistics are null and b) some are non-null. Error bars represent the standard errors after 1\,000 repeats of the experiment.}
    \label{table:inference_error_rate}
\end{table}
